---
title: "Results"
author: "Thao Le"
date: "2023-02-20"
output:
  html_document:
    keep_md: no
editor_options: 
  chunk_output_type: inline
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, fig.width = 12.5, fig.height = 8,
                      dev = c("png","pdf","tiff"),
                      dpi = 300)
```

```{r}
library(tidyverse)
library(survival)
library(gt)
library(flextable)
library(glue)
library(broom)
library(gtsummary)
library(here)
library(wesanderson)
library(patchwork)
library(RColorBrewer)
library(ggh4x)


# color and shape
# mycolor = c("#e41a1c", "#377eb8", "#4daf4a")
mycolor = wes_palette("Darjeeling1")[c(2,3,1)]
mycolor4 = c("#e41a1c", "#377eb8", "#4daf4a", "#984ea3")
# mycolor4 = c("#4daf4a", "#377eb8", "#e41a1c", "#984ea3")

myshape = c("–","o","+")
mypalette <- brewer.pal(n = 3, name = "YlOrRd")

# plot theme
old <- theme_set(theme_bw())
theme_update(axis.text.x = element_text(size = 12),
             axis.text.y = element_text(size = 12),
             strip.text.x = element_text(size = 12, colour = "darkblue"), 
             strip.text.y = element_text(size = 12, colour = "darkblue"),
             axis.title.y = element_text(size = 12),
             legend.text=element_text(size = 12))
# labels
interlength.labs <- c("High frequency", "Low frequency")
names(interlength.labs) <- c("0.5","1")

beta12.labs <- c("beta12 = -0.5", "beta12 = 0", "beta12 = 0.5")
names(beta12.labs) <- c("-0.5","0","0.5")

trans.labs <- c("Transition: 01","Transition: 02","Transition: 12")
names(trans.labs) <- c("01", "02", "12")

# load data
load("Interdata/2023-02-20_Bias-Results.Rdata") # constant 0.5, scale = 0.5
load("Interdata/2023-02-20_Nevents-Results.Rdata")
load("Interdata/2023-02-20_Simulation-Senarios.Rdata")
```

# Figure: true baseline hazards

```{r baselinefunction}
wfunc <- function(shape01, scale01 = 0.1, stime){shape01*scale01*stime^(shape01-1)}
stime = seq(from = 0, to = 5, length.out = 100)
baseline.alpha <- data.frame(time = stime,
                             alpha = c(rep(wfunc(shape01 = 1,scale01 = 0.1, stime = stime), each = 3),
                                       wfunc(shape01 = 1.5,scale01 = 0.1, stime = stime), 
                                       wfunc(shape01 = 1.2,scale01 = 0.1, stime = stime),
                                       wfunc(shape01 = 1.2,scale01 = 0.1, stime = stime),
                                       wfunc(shape01 = 1.5,scale01 = 0.1, stime = stime), 
                                       wfunc(shape01 = 1.5,scale01 = 0.1, stime = stime),
                                       wfunc(shape01 = 1.5,scale01 = 0.1, stime = stime)),
                             trans = c(rep(c("01","02","12"), each = 100),
                                       rep(c("01","02","12"), each = 100),
                                       rep(c("01","02","12"), each = 100)),
                             scen = rep(c("Low mortality","Moderate mortality","High mortality"), each = 300)
                             )
baseline.alpha$scen <- factor(baseline.alpha$scen, levels = c("Low mortality",
                                                              "Moderate mortality",
                                                              "High mortality"))
baseline.alpha %>% 
  ggplot(aes(time, alpha)) +
  geom_line() +
  facet_grid(scen ~ trans, 
             labeller = labeller(trans = trans.labs)) +
  labs(y = "Intensities",
       x = "Time")
```


```{r data}
# Calculate bias
## leave the cases shape12>shape02 out for now
bias.d <- all.bias %>% 
  # filter(false.positive.rate == 0) %>% 
  filter(shape12 == shape02) %>% 
  mutate(Scenarios = case_when(shape01 == 1 & shape02 == 1 & shape12 == 1 & beta01 == 0.5 & beta02 == 0 & beta12 == 0 ~ 1,
                               shape01 == 1 & shape02 == 1 & shape12 == 1 & beta01 == 0.5 & beta02 == 0 & beta12 == 0.5 ~ 2,
                               shape01 == 1 & shape02 == 1 & shape12 == 1 & beta01 == 0.5 & beta02 == 0.5 & beta12 == 0 ~ 3,
                               shape01 == 1 & shape02 == 1 & shape12 == 1 & beta01 == 0.5 & beta02 == 0.5 & beta12 == 0.5 ~ 4,
                               shape01 == 1 & shape02 == 1 & shape12 == 1 & beta01 == 0.5 & beta02 == 0 & beta12 == -0.5 ~ 5,
                               
                               shape01 == 1.5 & shape02 == 1.2 & shape12 == 1.2 & beta01 == 0.5 & beta02 == 0 & beta12 == 0 ~ 6,
                               shape01 == 1.5 & shape02 == 1.2 & shape12 == 1.2 & beta01 == 0.5 & beta02 == 0 & beta12 == 0.5 ~ 7,
                               shape01 == 1.5 & shape02 == 1.2 & shape12 == 1.2 & beta01 == 0.5 & beta02 == 0.5 & beta12 == 0 ~ 8,
                               shape01 == 1.5 & shape02 == 1.2 & shape12 == 1.2 & beta01 == 0.5 & beta02 == 0.5 & beta12 == 0.5 ~ 9,
                               shape01 == 1.5 & shape02 == 1.2 & shape12 == 1.2 & beta01 == 0.5 & beta02 == 0 & beta12 == -0.5 ~ 10,
                               
                               shape01 == 1.5 & shape02 == 1.5 & shape12 == 1.5 & beta01 == 0.5 & beta02 == 0 & beta12 == 0 ~ 11,
                               shape01 == 1.5 & shape02 == 1.5 & shape12 == 1.5 & beta01 == 0.5 & beta02 == 0 & beta12 == 0.5 ~ 12,
                               shape01 == 1.5 & shape02 == 1.5 & shape12 == 1.5 & beta01 == 0.5 & beta02 == 0.5 & beta12 == 0 ~ 13,
                               shape01 == 1.5 & shape02 == 1.5 & shape12 == 1.5 & beta01 == 0.5 & beta02 == 0.5 & beta12 == 0.5 ~ 14,
                               shape01 == 1.5 & shape02 == 1.5 & shape12 == 1.5 & beta01 == 0.5 & beta02 == 0 & beta12 == -0.5 ~ 15
  ),
  Scenarios_text = case_when(Scenarios %in% 1:5 ~ "Low mortality rates",
                             Scenarios %in% 6:10 ~ "Moderate mortality rates",
                             Scenarios %in% 10:15 ~ "High mortality rates"),
  Scenarios_text = factor(Scenarios_text, levels = c("Low mortality rates",
                                                     "Moderate mortality rates",
                                                     "High mortality rates")),
  Model = factor(Model, 
                 levels = c("true.w",
                            "W.lastvist",
                            "W.lastnegvisit",
                            "W.last2visit",
                            "W.deathtime",
                            "ic.lastvisit",
                            "ic.lastnegvisit",
                            "ic.last2visit",
                            "ic.deathtime",
                            "idm.lastvist",
                            "idm.lastnegvisit",
                            "idm.last2visit"),
                 labels = c("true",
                            "mp.LV",
                            "mp.LNV",
                            "mp.SLV",
                            "mp.D",
                            "ic.LV",
                            "ic.LNV",
                            "ic.SLV",
                            "ic.D",
                            "idm.LV",
                            "idm.LNV",
                            "idm.SLV"
                 ))
  ) %>% 
  filter(!is.na(Scenarios)) %>%
  filter(Model!= "true") %>% 
  ungroup()
```

# Fig: Number of events

```{r noEvents}
plot.d <- all.events %>% 
  mutate(Scenarios = case_when(shape01 == 1 & shape02 == 1 & shape12 == 1 & beta01 == 0.5 & beta02 == 0 & beta12 == 0 ~ 1,
                               shape01 == 1 & shape02 == 1 & shape12 == 1 & beta01 == 0.5 & beta02 == 0 & beta12 == 0.5 ~ 2,
                               shape01 == 1 & shape02 == 1 & shape12 == 1 & beta01 == 0.5 & beta02 == 0.5 & beta12 == 0 ~ 3,
                               shape01 == 1 & shape02 == 1 & shape12 == 1 & beta01 == 0.5 & beta02 == 0.5 & beta12 == 0.5 ~ 4,
                               shape01 == 1 & shape02 == 1 & shape12 == 1 & beta01 == 0.5 & beta02 == 0 & beta12 == -0.5 ~ 5,
                               
                               shape01 == 1.5 & shape02 == 1.2 & shape12 == 1.2 & beta01 == 0.5 & beta02 == 0 & beta12 == 0 ~ 6,
                               shape01 == 1.5 & shape02 == 1.2 & shape12 == 1.2 & beta01 == 0.5 & beta02 == 0 & beta12 == 0.5 ~ 7,
                               shape01 == 1.5 & shape02 == 1.2 & shape12 == 1.2 & beta01 == 0.5 & beta02 == 0.5 & beta12 == 0 ~ 8,
                               shape01 == 1.5 & shape02 == 1.2 & shape12 == 1.2 & beta01 == 0.5 & beta02 == 0.5 & beta12 == 0.5 ~ 9,
                               shape01 == 1.5 & shape02 == 1.2 & shape12 == 1.2 & beta01 == 0.5 & beta02 == 0 & beta12 == -0.5 ~ 10,
                               
                               shape01 == 1.5 & shape02 == 1.5 & shape12 == 1.5 & beta01 == 0.5 & beta02 == 0 & beta12 == 0 ~ 11,
                               shape01 == 1.5 & shape02 == 1.5 & shape12 == 1.5 & beta01 == 0.5 & beta02 == 0 & beta12 == 0.5 ~ 12,
                               shape01 == 1.5 & shape02 == 1.5 & shape12 == 1.5 & beta01 == 0.5 & beta02 == 0.5 & beta12 == 0 ~ 13,
                               shape01 == 1.5 & shape02 == 1.5 & shape12 == 1.5 & beta01 == 0.5 & beta02 == 0.5 & beta12 == 0.5 ~ 14,
                               shape01 == 1.5 & shape02 == 1.5 & shape12 == 1.5 & beta01 == 0.5 & beta02 == 0 & beta12 == -0.5 ~ 15
  ),
   Scenarios_text = case_when(Scenarios %in% 1:5 ~ "Low mortality rates",
                             Scenarios %in% 6:10 ~ "Moderate mortality rates",
                             Scenarios %in% 10:15 ~ "High mortality rates"),
  Scenarios_text = factor(Scenarios_text, levels = c("Low mortality rates",
                                                     "Moderate mortality rates",
                                                     "High mortality rates"))) %>% 
  filter(!is.na(Scenarios)) %>% 
  pivot_longer(cols = c(n.persist, n.death.obs),
               names_to = "eventype")

# beta label
plot.d$Facet_beta02 = paste('beta["02"]*\"=', plot.d$beta02, "\"")
plot.d$Facet_beta12 = paste('beta[12]*\"=', plot.d$beta12, "\"")
plot.d %>% 
  ggplot(aes(as.factor(Scenarios), value, fill = eventype)) +
  geom_boxplot() +
  facet_grid2(inspectLength ~ Scenarios_text + Facet_beta02 + Facet_beta12,
              strip = strip_nested(),
              scales = "free_x", 
              labeller = labeller(inspectLength = interlength.labs,
                                  Facet_beta02 = label_parsed,
                                  Facet_beta12 = label_parsed),
) +
  theme(legend.position = "top") +
  labs(y = "Number of events",
       x = "Scenarios") +
  scale_fill_manual(name = "",
                    values = mycolor,
                    labels = c("Observed death",
                               "Observed disease")) 
```

# Fig: average bias

```{r avgBias}
plot.d <- bias.d %>% 
   mutate(Model.type = case_when(grepl("mp.", Model) ~ "Competing risk, midpoint",
                                grepl("ic.", Model) ~ "Competing risk, IC",
                                grepl("idm.", Model) ~ "Illness death model"),
         censor.type = gsub(pattern = ".*\\.", replacement = "", x = Model),
         Scenarios = factor(Scenarios, levels = c(1,6,11,
                                                  3,8,13,
                                                  2,7,12,
                                                  4,9,14,
                                                  5,10,15)))
# beta label
plot.d$Facet_beta02 = paste('beta["02"]*\"=', plot.d$beta02, "\"")
plot.d$Facet_beta12 = paste('beta[12]*\"=', plot.d$beta12, "\"")

plot.d %>%
  filter(false.positive.rate == 0) %>%
  ggplot(aes(Scenarios, mean.bias)) +
  # geom_line(aes(group = Model,
  #               col = as.factor(censor.type))) +
  geom_point(aes(col = as.factor(censor.type),
                 shape = Scenarios_text),
             size = 2) +
  scale_color_manual(name = "Censor type",
                     values = mycolor4
  ) +
  scale_shape_manual(name = "Scenario",
                     values = c(17,15,16)) +
  theme(legend.position = "top", ) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  facet_grid2(inspectLength ~ Model.type + Facet_beta02 + Facet_beta12,
              scales = "free",
              space = "free_y",
              switch = "y",
              strip = strip_nested(),
              labeller = labeller(inspectLength = interlength.labs,
                                  Facet_beta02 = label_parsed,
                                  Facet_beta12 = label_parsed)
          ) + 
  labs(y = "Estimated bias") +
  geom_line(aes(group = Model,
                col = as.factor(censor.type)),
            # alpha = 0.8,
            linetype = "dotted") 
```

# Fig: coverage

```{r coverage}
plot.d %>% 
  filter(false.positive.rate == 0) %>%
  ggplot(aes(Scenarios, mean.coverage)) +
  geom_line(aes(group = Model,
                col = as.factor(censor.type)),
            linetype = "dotted") +
  geom_point(aes(col = as.factor(censor.type),
                 shape = Scenarios_text),
             size = 2) +
  scale_color_manual(name = "Censor type",
                     values = mycolor4
  ) +
  scale_shape_manual(name = "Scenario",
                     values = c(17,15,16)) +
  theme(legend.position = "top", ) +
  # scale_x_continuous(breaks = c(1:15)) +
  geom_hline(yintercept = 0.95, linetype = "dashed", alpha = 0.5) +
  facet_grid2(inspectLength ~ Model.type + Facet_beta02 + Facet_beta12,
              scales = "free",
              space = "free_y",
              switch = "y",
              strip = strip_nested(),
              labeller = labeller(inspectLength = interlength.labs,
                                  Facet_beta02 = label_parsed,
                                  Facet_beta12 = label_parsed)
          )  +
  labs(y = "Coverage")

```

# Fig: average bias and confidence interval

```{r avgBiasCI}
p1 <- bias.d %>% 
  filter(false.positive.rate == 0) %>% 
  filter(inspectLength == 0.5) %>% 
  select( Model, mean.bias, upper.ci, lower.ci, Scenarios, Scenarios_text) %>% 
  ggplot(aes(y=Model, x=mean.bias, xmin=lower.ci, xmax=upper.ci)) +
  geom_pointrange(size = 0.1) +
  ylab("Model") +
  xlab("Estimated bias") +
  facet_wrap( ~ Scenarios , 
             ncol = 5) +
  # facet_grid(Scenarios_text ~ Scenarios, scales = "free_y") +
  geom_vline(xintercept = 0, 
             color = "grey",
             linetype = "dashed")

# plot for low visit frequency
p2 <- bias.d %>% 
  filter(false.positive.rate == 0) %>% 
  filter(inspectLength == 1) %>% 
  select( Model, mean.bias, upper.ci, lower.ci, Scenarios, Scenarios_text) %>% 
  ggplot(aes(y=Model, x=mean.bias, xmin=lower.ci, xmax=upper.ci)) +
  geom_pointrange(size = 0.1) +
  ylab("Model") +
  xlab("Estimated bias") +
  facet_wrap( ~ Scenarios , 
             ncol = 5) +
  # facet_grid(Scenarios_text ~ Scenarios, scales = "free_y") +
  geom_vline(xintercept = 0, 
             color = "grey",
             linetype = "dashed")

p1 + labs(title = "A) High frequency visit") 
p2 + labs(title = "B) Low frequency visit") 
```

# Fig: average bias in the presence of false positive tests

```{r avgBiasIDMFaslePositive}
plot.d %>% 
  filter(grepl("idm", Model)) %>% 
  ggplot(aes(Scenarios, mean.bias)) +
  geom_line(aes(group = as.factor(false.positive.rate),
                col = as.factor(false.positive.rate)),
            linetype = "dotted") +
  geom_point(aes(col = as.factor(false.positive.rate)),
             size = 2) +
  scale_color_manual(name = "False positive rate",
                     values = mycolor4
  ) +
  scale_shape_manual(name = "Scenario",
                     values = c(17,15,16,1)) +
  theme(legend.position = "top", ) +
  # scale_x_continuous(breaks = c(1:15)) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  facet_grid2(inspectLength ~ Model + Facet_beta02 + Facet_beta12,
              scales = "free",
              space = "free_y",
              switch = "y",
              strip = strip_nested(),
              labeller = labeller(inspectLength = interlength.labs,
                                  Facet_beta02 = label_parsed,
                                  Facet_beta12 = label_parsed)
  )  +
  labs(y = "Estimated bias")
```


# Fig: Amount of false positive test

```{r AmountFP}
load("./Interdata/2023-02-20_simresults-Fasel-Positive-Rate.Rdata")

# combine
events.all <- events %>% 
  mutate(scenario = as.numeric(scenario)) %>% 
  left_join(scenarios %>% mutate(scenario = row_number())) %>% 
  filter(shape12 == shape02) %>% 
  mutate(Scenarios = case_when(shape01 == 1 & shape02 == 1 & shape12 == 1 & beta01 == 0.5 & beta02 == 0 & beta12 == 0 ~ 1,
                               shape01 == 1 & shape02 == 1 & shape12 == 1 & beta01 == 0.5 & beta02 == 0 & beta12 == 0.5 ~ 2,
                               shape01 == 1 & shape02 == 1 & shape12 == 1 & beta01 == 0.5 & beta02 == 0.5 & beta12 == 0 ~ 3,
                               shape01 == 1 & shape02 == 1 & shape12 == 1 & beta01 == 0.5 & beta02 == 0.5 & beta12 == 0.5 ~ 4,
                               shape01 == 1 & shape02 == 1 & shape12 == 1 & beta01 == 0.5 & beta02 == 0 & beta12 == -0.5 ~ 5,
                               
                               shape01 == 1.5 & shape02 == 1.2 & shape12 == 1.2 & beta01 == 0.5 & beta02 == 0 & beta12 == 0 ~ 6,
                               shape01 == 1.5 & shape02 == 1.2 & shape12 == 1.2 & beta01 == 0.5 & beta02 == 0 & beta12 == 0.5 ~ 7,
                               shape01 == 1.5 & shape02 == 1.2 & shape12 == 1.2 & beta01 == 0.5 & beta02 == 0.5 & beta12 == 0 ~ 8,
                               shape01 == 1.5 & shape02 == 1.2 & shape12 == 1.2 & beta01 == 0.5 & beta02 == 0.5 & beta12 == 0.5 ~ 9,
                               shape01 == 1.5 & shape02 == 1.2 & shape12 == 1.2 & beta01 == 0.5 & beta02 == 0 & beta12 == -0.5 ~ 10,
                               
                               shape01 == 1.5 & shape02 == 1.5 & shape12 == 1.5 & beta01 == 0.5 & beta02 == 0 & beta12 == 0 ~ 11,
                               shape01 == 1.5 & shape02 == 1.5 & shape12 == 1.5 & beta01 == 0.5 & beta02 == 0 & beta12 == 0.5 ~ 12,
                               shape01 == 1.5 & shape02 == 1.5 & shape12 == 1.5 & beta01 == 0.5 & beta02 == 0.5 & beta12 == 0 ~ 13,
                               shape01 == 1.5 & shape02 == 1.5 & shape12 == 1.5 & beta01 == 0.5 & beta02 == 0.5 & beta12 == 0.5 ~ 14,
                               shape01 == 1.5 & shape02 == 1.5 & shape12 == 1.5 & beta01 == 0.5 & beta02 == 0 & beta12 == -0.5 ~ 15
  ),
  Scenarios_text = case_when(Scenarios %in% 1:5 ~ "Low mortality rates",
                             Scenarios %in% 6:10 ~ "Moderate mortality rates",
                             Scenarios %in% 10:15 ~ "High mortality rates"),
  Scenarios_text = factor(Scenarios_text, levels = c("Low mortality rates",
                                                     "Moderate mortality rates",
                                                     "High mortality rates")))
tmp <- events.all %>% 
  mutate(
    pct1 = n.event.incorrect.time/n.event*100,
    pct2 = n.event.would.not.obverve/n.event*100,
    Scenarios = factor(Scenarios, levels = c(1,6,11,
                                             3,8,13,
                                             2,7,12,
                                             4,9,14,
                                             5,10,15))
  ) %>% 
  select(Scenarios_text, Scenarios, inspectLength, contains("pct"), beta12, beta02) %>% 
  pivot_longer(cols = c(pct1, pct2), names_to = "pct") %>% 
  mutate(pct = factor(pct, levels = c("pct1", "pct2"),
                         label = c("Incorrect event time", "Additional events")))
tmp %>% 
  group_by(inspectLength, Scenarios_text ,pct) %>% 
  summarise(m = mean(value))

tmp$Facet_beta02 = paste('beta["02"]*\"=', tmp$beta02, "\"")
tmp$Facet_beta12 = paste('beta[12]*\"=', tmp$beta12, "\"")
tmp %>% 
  ggplot(aes(Scenarios, value)) +
  geom_boxplot(aes(color = Scenarios_text,
                   fill = as.factor(pct)
                   )) +
  theme(legend.position = "top") +
  labs(y = "Percentage",
       x = "Scenarios") +
  scale_fill_manual(name = "",
                    values = c("white", "grey")) +
  scale_color_manual(name = "",
                    values = mycolor4) +
   facet_grid2(inspectLength ~ Facet_beta02 + Facet_beta12,
              scales = "free",
              space = "free_y",
              switch = "y",
              strip = strip_nested(),
              labeller = labeller(inspectLength = interlength.labs,
                                  Facet_beta02 = label_parsed,
                                  Facet_beta12 = label_parsed)
  ) 


```


# Table: Failed simulation

```{r}
bias.d %>% 
 filter(false.positive.rate == 0) %>% 
  filter(Model == "idm.SLV") %>% 
  mutate(npct = style_percent((1000 - n.sim)/1000)) %>% 
  select(npct, Scenarios, inspectLength) %>%
  arrange(Scenarios) %>%
  pivot_wider(names_from = "inspectLength", 
              values_from = npct, names_glue = "visitlength_{inspectLength}") %>% 
  flextable() %>% 
  set_header_labels(values = list(visitlength_0.5 = "High frequency",
                                  visitlength_1 = "Low frequency")) %>% 
  autofit() %>% align(align = "center", part = "all")  %>% 
  set_caption("Failed simulation (percentage) for the idm.SLV model")
```

# Table: ASPREE data,  Number of events

This table requires aspree data to populate

```{r, eval = FALSE}
library(gtsummary)
all.d %>% 
  ungroup() %>% 
  select(event, obs.d, Diab_deriv) %>% 
  mutate(death.without.pd = obs.d == 1 & event == 0,
         death.with.pd = obs.d == 1 & event == 1,
         pd.without.death = obs.d == 0 & event == 1) %>% 
  tbl_summary(by = Diab_deriv) %>% 
  add_overall()
```

# Table: regression coeficient of aspree data

```{r, aspree-result, fig.width=8, fig.height=7}
load(("./Interdata/2023-01-18_aspree-idm.Rdata"))


# extract HR for cox models
coxmodels <- bind_rows(lapply(list(censordead, lastvisit, lasttest, lastsecondvisit,
                             censordead.mp, lastvisit.mp, lasttest.mp, lastsecondvisit.mp), 
                        function(x) tidy(x, 
                                         exponentiate = TRUE, 
                                         conf.int = TRUE))) %>% 
  mutate(model = c("fd.D","fd.LV","fd.LNV","fd.SLV",
                   "mp.D","mp.LV","mp.LNV","mp.SLV"),
         beta = style_number(log(estimate), 2),
         estimate = style_number(estimate, 2),
         "95% CI" = glue("{style_number(conf.low, 2)}; {style_number(conf.high,2)}")) %>% 
  select(model, beta, estimate, "95% CI", conf.low, conf.high) %>% 
  rename("HR" = "estimate")

# extract HR for IC models
icmodels <- bind_rows(lapply(list(ic.death, ic.lastvisit, ic.lastnegvisit, ic.last2visit), function(x){
  data.frame(beta = coef(x),
             conf.low = exp(confint(x)[1]),
             conf.high = exp(confint(x)[2]))
})) %>% 
  mutate(model = c("ic.D","ic.LV","ic.LNV","ic.SLV"),
         HR = style_number(exp(beta), 2),
         # HR = exp(beta),
         beta = style_number(beta, 2),
         "95% CI" = glue("{style_number(exp(conf.low), 2)}; {style_number(exp(conf.high),2)}")) %>% 
  select(model, beta, HR, "95% CI", conf.low, conf.high) 
rownames(icmodels) <- NULL

# extract HR for idm model
extract.idm.HR <- function(idmfit, transition = 1){
  data.frame(beta = style_number(idmfit$coef[transition],2),
             HR = style_number(idmfit$HR[transition],2),
             # HR = idmfit$HR[transition],
             conf.low = exp(idmfit$coef[transition] - qnorm(0.975)*idmfit$se[transition]),
             conf.high = exp(idmfit$coef[transition] + qnorm(0.975)*idmfit$se[transition]))
}

# idm.fit and idmfit.LSecV are the same
idms <- bind_rows(lapply(list(idmfit.LV, idmfit.LNegV, idmfit.LSecV), function(x) extract.idm.HR(x))) %>% 
  mutate(model = c("idm.LV", "idm.LNV", "idm.SLV"))
rownames(idms) <- NULL
idms <- idms %>% 
  mutate( "95% CI" = glue("{style_number(conf.low, 2)}; {style_number(conf.high,2)}"))

# coefficient from other transition
idms1 <- bind_rows(lapply(list(idmfit.LV,idmfit.LNegV,idmfit.LSecV), function(x) extract.idm.HR(x, transition = 2))) %>% 
  mutate(model = c("idm.LV", "idm.LNV", "idm.SLV"))
rownames(idms1) <- NULL
idms1 <- idms1 %>% 
  mutate( "95% CI" = glue("{style_number(conf.low, 2)}; {style_number(conf.high,2)}"))

idms2 <- bind_rows(lapply(list(idmfit.LV,idmfit.LNegV,idmfit.LSecV), function(x) extract.idm.HR(x, transition = 3))) %>% 
  mutate(model = c("idm.LV", "idm.LNV", "idm.SLV"))
rownames(idms2) <- NULL
idms2 <- idms2 %>% 
   mutate( "95% CI" = glue("{style_number(conf.low, 2)}; {style_number(conf.high,2)}"))


# Table 
coef.tab <- rbind(subset(coxmodels, select = c("model","beta", "HR", "95% CI")),
                  subset(icmodels, select = c("model", "beta","HR", "95% CI")),
                  subset(idms, select = c("model", "beta","HR", "95% CI")))
coef.tab1 <- rbind(subset(idms1, select = c("model","beta", "HR", "95% CI")),
                  subset(idms2, select = c("model", "beta","HR", "95% CI")))

```

Wide table format

```{r}
# try long table
coef.d <- rbind(coef.tab, coef.tab1) 
aspreetab <- rbind(coef.tab, coef.tab1) %>% 
  mutate(trans = rep(c("01","02","12"), c(15,3,3))) %>% 
  pivot_wider(names_from = trans, values_from = c(beta, HR, "95% CI")) %>% 
  gt() %>% 
   tab_spanner(label = md("Transition 0 -> 1"), 
              columns = c(contains("01"))) %>% 
  tab_spanner(label = md("Transition 0 -> 2"), 
              columns = c(contains("02"))) %>% 
  tab_spanner(label = md("Transition 1 -> 2"), 
              columns = c(contains("12"))) %>% 
  sub_missing(
  columns = everything(),
  rows = everything(),
  missing_text = "---"
) %>% 
  cols_label(beta_01 = "beta",
             beta_02 = "beta",
             beta_12 = "beta",
             HR_01 = "HR",
             HR_02 = "HR",
             HR_12 = "HR",
             "95% CI_01" = "95% CI",
             "95% CI_02" = "95% CI",
             "95% CI_12" = "95% CI") 
  # basic_theme()
aspreetab 
```

